Forecasting Influenza Hospitalizations Using a Bayesian Hierarchical Nonlinear Model with Discrepancy

### 2025-12-03 manuscript_res.tex
clean up section 3.7

\begin{table}[ht]
\centering
% \begin{adjustwidth}{-3cm}{-1.5cm}
\caption{Overall summary scores for each of the 13 non-ensemble FluSight
models with over 80\% submissions and 
the ASGD\_NORM2 and SIRD\_NORM2 models. 
Summaries include mean weighted interval
and log-weighted interval scores (MWIS/MLWIS), 
mean squared error
difference between predictive model empirical and theoretical coverage (MSEC)
see figure \ref{fig:lwis_cover_sum} c)), percentage of forecasts for all 
targets during the 2023 season (\% Forcs), and relative weighted interval
and log-weighted interval scores (RWIS/RLWIS).
\\}
\small
\begin{tabular}{lrrrrrrrr}
  % \hline
                              & MWIS & MLWIS & MSEC  & \% Forcs & RWIS & RLWIS\\ 
  \hline 
ASGD\_NORM2                   & 62   & 0.34  & 0.001 & 100      & 1    & 1 \\ 
  PSI-PROF                    & 63   & 0.35  & 0.003 & 100      & 0.90 & 0.97 \\ 
  SIRD\_NORM2                 & 67   & 0.36  & 0.001 & 100      & 0.93 & 0.95 \\
  CEPH-Rtrend\_fluH           & 69   & 0.39  & 0.004 & 100      & 0.81 & 0.86 \\ 
  FluSight-baseline           & 85   & 0.41  & 0.023 & 100      & 0.63 & 0.82 \\ 
  UM-DeepOutbreak             & 83   & 0.46  & 0.010 & 99       & 0.64 & 0.72 \\ 
  cfarenewal-cfaepimlight     & 76   & 0.37  & 0.001 & 99       & 0.72 & 0.92 \\ 
  MOBS-GLEAM\_FLUH            & 66   & 0.35  & 0.021 & 98       & 0.87 & 0.95 \\ 
  LosAlamos\_NAU-CModel\_Flu  & 242  & 0.64  & 0.153 & 93       & 0.21 & 0.53 \\ 
  UGuelph-CompositeCurve      & 132  & 0.52  & 0.018 & 93       & 0.43 & 0.62 \\ 
  LUcompUncertLab-chimera     & 84   & 0.43  & 0.004 & 92       & 0.67 & 0.71 \\ 
  UGA\_flucast-INFLAenza      & 74   & 0.32  & 0.003 & 90       & 0.77 & 1.07 \\ 
  cfa-flumech                 & 101  & 0.41  & 0.019 & 89       & 0.58 & 0.85 \\ 
  UGA\_flucast-Copycat        & 76   & 0.35  & 0.012 & 87       & 0.81 & 0.98 \\ 
  GT-FluFNP                   & 105  & 0.48  & 0.046 & 86       & 0.45 & 0.73 \\ 
  % UNC\_IDD-InfluPaint         & 107 & 0.35 & 16 & 0.24 & 0.043 & 78 & 0.58 & 0.95 \\ 
  % NU\_UCSD-GLEAM\_AI\_FLUH    & 98 & 0.39 & 22 & 0.24 & 0.014 & 74 & 0.68 & 0.83 \\ 
  % SigSci-CREG                 & 59 & 0.49 & 12 & 0.31 & 0.018 & 71 & 0.62 & 0.74 \\ 
  % PSI-PROF\_beta              & 77 & 0.32 & 18 & 0.20 & 0.004 & 67 & 0.87 & 0.93 \\ 
  % NIH-Flu\_ARIMA              & 230 & 0.34 & 28 & 0.23 & 0.001 & 20 & 0.57 & 0.88 \\ 
  % GH-model                    & 161 & 1.52 & 28 & 1.47 & 0.373 & 17 & 0.18 & 0.27 \\ 
  % UGA\_flucast-OKeeffe        & 27 & 0.59 & 8 & 0.43 & 0.003 & 10 & 0.60 & 0.58 \\  
\end{tabular}
% \end{adjustwidth}
\label{tab:fin_analysis_stats}
\end{table}

>>>>

% \begin{table}[ht]
% \centering
% % \begin{adjustwidth}{-3cm}{-1.5cm}
% \caption{Overall summary scores for each of the 13 non-ensemble FluSight
% models with over 80\% submissions and 
% the ASGD\_NORM2 and SIRD\_NORM2 models. 
% Summaries include mean weighted interval
% and log-weighted interval scores (MWIS/MLWIS), 
% mean squared error
% difference between predictive model empirical and theoretical coverage (MSEC)
% see figure \ref{fig:lwis_cover_sum} c)), percentage of forecasts for all 
% targets during the 2023 season (\% Forcs), and relative weighted interval
% and log-weighted interval scores (RWIS/RLWIS).
% \\}
% \small
% \begin{tabular}{lrrrrrrrr}
%   % \hline
%                               & MWIS & MLWIS & MSEC  & \% Forcs & RWIS & RLWIS\\ 
%   \hline 
% ASGD\_NORM2                   & 62   & 0.34  & 0.001 & 100      & 1    & 1 \\ 
%   PSI-PROF                    & 63   & 0.35  & 0.003 & 100      & 0.90 & 0.97 \\ 
%   SIRD\_NORM2                 & 67   & 0.36  & 0.001 & 100      & 0.93 & 0.95 \\
%   CEPH-Rtrend\_fluH           & 69   & 0.39  & 0.004 & 100      & 0.81 & 0.86 \\ 
%   FluSight-baseline           & 85   & 0.41  & 0.023 & 100      & 0.63 & 0.82 \\ 
%   UM-DeepOutbreak             & 83   & 0.46  & 0.010 & 99       & 0.64 & 0.72 \\ 
%   cfarenewal-cfaepimlight     & 76   & 0.37  & 0.001 & 99       & 0.72 & 0.92 \\ 
%   MOBS-GLEAM\_FLUH            & 66   & 0.35  & 0.021 & 98       & 0.87 & 0.95 \\ 
%   LosAlamos\_NAU-CModel\_Flu  & 242  & 0.64  & 0.153 & 93       & 0.21 & 0.53 \\ 
%   UGuelph-CompositeCurve      & 132  & 0.52  & 0.018 & 93       & 0.43 & 0.62 \\ 
%   LUcompUncertLab-chimera     & 84   & 0.43  & 0.004 & 92       & 0.67 & 0.71 \\ 
%   UGA\_flucast-INFLAenza      & 74   & 0.32  & 0.003 & 90       & 0.77 & 1.07 \\ 
%   cfa-flumech                 & 101  & 0.41  & 0.019 & 89       & 0.58 & 0.85 \\ 
%   UGA\_flucast-Copycat        & 76   & 0.35  & 0.012 & 87       & 0.81 & 0.98 \\ 
%   GT-FluFNP                   & 105  & 0.48  & 0.046 & 86       & 0.45 & 0.73 \\ 
%   % UNC\_IDD-InfluPaint         & 107 & 0.35 & 16 & 0.24 & 0.043 & 78 & 0.58 & 0.95 \\ 
%   % NU\_UCSD-GLEAM\_AI\_FLUH    & 98 & 0.39 & 22 & 0.24 & 0.014 & 74 & 0.68 & 0.83 \\ 
%   % SigSci-CREG                 & 59 & 0.49 & 12 & 0.31 & 0.018 & 71 & 0.62 & 0.74 \\ 
%   % PSI-PROF\_beta              & 77 & 0.32 & 18 & 0.20 & 0.004 & 67 & 0.87 & 0.93 \\ 
%   % NIH-Flu\_ARIMA              & 230 & 0.34 & 28 & 0.23 & 0.001 & 20 & 0.57 & 0.88 \\ 
%   % GH-model                    & 161 & 1.52 & 28 & 1.47 & 0.373 & 17 & 0.18 & 0.27 \\ 
%   % UGA\_flucast-OKeeffe        & 27 & 0.59 & 8 & 0.43 & 0.003 & 10 & 0.60 & 0.58 \\  
% \end{tabular}
% % \end{adjustwidth}
% \label{tab:fin_analysis_stats}
% \end{table}
